---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE }
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

#packages
library(magick)
library(tidyverse)

```

```{css}

body {
  background-color: lightgrey;
  padding: 40px;
}

p {
  color: black;
}


h2 {
  color: white;
  font-weight: bold;
  underline: white
}
  
```

## Dynamic Tracking of Shoe Characteristics

This dynamic report intends to analyse the characteristics of different shoes I saw people wearing. The nature of my data is observational. During the observation period, every time I left my house, I would note down 3 characteristics about the first pair of shoes other I saw someone wearing. Two of these characteristics are categorical variables; the shoe brand and what type of shoe it was. The third charecteristic was a numeric variable; specifically how many different colours were on the shoe.


```{r fig.width = 8, fig.height = 4}

#graphs

csv_file <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vS0Lz3R3oVtqlawNFPUTUTQ4M9m5sIJb8R1DcLSCcnrqQ8c7veAXuh5dwuK--AoM3NEwv9XcefPlb3B/pub?output=csv"

logged_data <- read_csv(csv_file)

latest_data <- logged_data %>%
  rename(shoe_brand = 2,
         shoe_colours = 3,
         shoe_type = 4)

latest_data %>%
  ggplot() +
  geom_bar(aes(y = shoe_brand, fill = shoe_type)) +
  labs (title = "Graphing the sole trend",
        subtitle = "Observed Frequency of Different Shoe Brands",
        caption = "Source: Google Forms",
        x = "Frequency Observed",
        y = "Shoe Brand")

latest_data %>%
  ggplot() +
  geom_bar(aes(y = shoe_colours, fill = shoe_brand)) +
  labs (title = "Tracking shoe hues",
        subtitle = "Observed Frequency of Different Amounts of Colours on Shoes",
        caption = "Source: Google Forms",
        x = "Frequency Observed",
        y = "Amount of Different Colours on Shoe")


#dynamic comments

#comment 1
shoe_colour_observations <- length(latest_data$shoe_colours)

mean_colour_count <- mean(latest_data$shoe_colours) %>% round(1)

paste0("The mean number of different colours on a pair of shoes reported by the ", shoe_colour_observations, " observations in the Google Form was ", mean_colour_count, ".")


#comment 2
shoe_colour_observations2 <- length(latest_data$shoe_colours)

max_colour_count <- max(latest_data$shoe_colours) %>% round(1)

paste0("The maximum number of different colours on a pair of shoes reported by the ", shoe_colour_observations, " observations in the Google Form was ", max_colour_count, ".")


#comment 3
shoe_colour_observations3 <- length(latest_data$shoe_colours)

min_colour_count <- min(latest_data$shoe_colours) %>% round(1)

paste0("The minimum number of different colours on a pair of shoes reported by the ", shoe_colour_observations, " observations in the Google Form was ", min_colour_count, ".")
```
```{r}



